Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System

### 2016-12-02 manuscript.tex
20161202

&\bar m l^2\phi''+2\bar m \phi'l'l+\bar m l^2\sin\phi\cos\phi\left[(\theta'+\Omega)^2+3\bar m \Omega\cos^2\theta\right]=\tau_\phi+\tau_{\phi d},\label{eq:dynamics 1}

@@

Based on the novel dimensionless transformations~(\ref{eq:varcon}), Eq.~(\ref{eq:dynamics 1}) can be converted into the dimensionless Euler-Lagrange dynamical equation described as follows:
\begin{align}
H(\bm q)\ddot {\bm q}+C(\bm q,\dot{\bm q})\dot{\bm q}+G(\bm q) = \bm\tau+\bm\tau_d,\label{eq:dynamic model}
\end{align}
where
\begin{align}
\begin{split}
\bm q&= \begin{pmatrix}\lambda&\theta&\phi\end{pmatrix}^T\\
\bm \tau&=\begin{pmatrix}\hat\tau_t&\hat\tau_\theta&\hat\tau_\phi\end{pmatrix}^T\\
\bm\tau_d&=\begin{pmatrix}\hat\tau_{td}&\hat\tau_{\theta d}&\hat\tau_{\phi d}\end{pmatrix}^T\\
H(\bm q) &= \begin{bmatrix}1 &0&0\\0 &\lambda^2\cos^2\phi&0\\0&0&\lambda^2\end{bmatrix}\\
C(\bm q,\dot{\bm q}) &=\begin{bmatrix}0 &-(\lambda\dot \theta+2\lambda)\cos^2\phi&-\lambda\dot\phi\\(2\lambda+\lambda\dot \theta)\cos^2\phi&\lambda\dot \lambda\cos^2\phi-\lambda^2\dot\phi\sin\phi\cos\phi&-(\dot\theta+2)\lambda^2\sin\phi\cos\phi\\ \lambda\dot\phi&\lambda^2(\dot\theta+2)\sin\phi\cos\phi&\lambda\dot \lambda\end{bmatrix}\\
G(\bm q) &=\begin{bmatrix}-\lambda\cos^2\phi+2\lambda+3\lambda\cos ^2\theta\cos^2\phi\\3\lambda^2\cos\theta\sin\theta\cos^2\phi\\\lambda^2+3\lambda^2\cos^2\theta\sin\phi\cos\phi\end{bmatrix}.
\end{split}
\end{align}
Based on the expression above, one can find that $\dot H(\bm q) - 2C(\bm q,\dot{\bm q})$ is skew-symmetric, namely,
\begin{align}
\bm q^T(\dot H(\bm q) - 2C(\bm q,\dot{\bm q}))\bm q = 0.
\end{align}
\begin{myrem}

>>>>

&\bar m l^2\phi''+2\bar m \phi'l'l+\bar m l^2\sin\phi\cos\phi\left[(\theta'+\Omega)^2+3\bar m \Omega^2\cos^2\theta\right]=\tau_\phi+\tau_{\phi d},\label{eq:dynamics 1}

@@

Based on the novel dimensionless transformations~(\ref{eq:varcon}), Eq.~(\ref{eq:dynamics 1}) can be converted into the dimensionless Euler-Lagrange dynamical equation described as follows:
\begin{align}
H(\bm q)\ddot {\bm q}+C(\bm q,\dot{\bm q})\dot{\bm q}+G(\bm q) = \bm\tau+\bm\tau_d,\label{eq:dynamic model}
\end{align}
where
\begin{align}
\begin{split}
\bm q&= \begin{pmatrix}\lambda&\theta&\phi\end{pmatrix}^T\\
\bm \tau&=\begin{pmatrix}\hat\tau_t&\hat\tau_\theta&\hat\tau_\phi\end{pmatrix}^T\\
\bm\tau_d&=\begin{pmatrix}\hat\tau_{td}&\hat\tau_{\theta d}&\hat\tau_{\phi d}\end{pmatrix}^T\\
H(\bm q) &= \begin{bmatrix}1 &0&0\\0 &\lambda^2\cos^2\phi&0\\0&0&\lambda^2\end{bmatrix}\\
C(\bm q,\dot{\bm q}) &=\begin{bmatrix}0 &-(\lambda\dot \theta+2\lambda)\cos^2\phi&-\lambda\dot\phi\\(2\lambda+\lambda\dot \theta)\cos^2\phi&\lambda\dot \lambda\cos^2\phi-\lambda^2\dot\phi\sin\phi\cos\phi&-(\dot\theta+2)\lambda^2\sin\phi\cos\phi\\ \lambda\dot\phi&\lambda^2(\dot\theta+2)\sin\phi\cos\phi&\lambda\dot \lambda\end{bmatrix}\\
G(\bm q) &=\begin{bmatrix}-\lambda\cos^2\phi+2\lambda+3\lambda\cos ^2\theta\cos^2\phi\\3\lambda^2\cos\theta\sin\theta\cos^2\phi\\(1+3\cos^2\theta)\lambda^2\sin\phi\cos\phi\end{bmatrix}.
\end{split}
\end{align}
Based on the expression above, one can find that $\dot H(\bm q) - 2C(\bm q,\dot{\bm q})$ is skew-symmetric, namely,
\begin{align}
\bm q^T(\dot H(\bm q) - 2C(\bm q,\dot{\bm q}))\bm q = 0.
\end{align}
\begin{myrem}
